\papertitle

### 2014-03-17 final-report/paper.tex
Added images folder
More future work

>>>>

Besides performance improvements, we plan to integrate X-trace and its visualization to offer the orthogonal view and allow users to trace how tuple batches flow through the operators and between operators. Combined with the visualizations described in this paper, it will form a powerful debugging tool that will help us to better understand and improve query execution.
